6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Fixed up references

The rise in software complexity together with ever changing business demands during its development has given rise to a number of popular methodologies or techniques in research and industry, such as Model Driven Development~\cite{MDD}, Extreme Programming~\cite{BeckXP} and the Agile movement~\cite{AgileManifesto}.

@@

Test Driven Development (TDD) has surged in popularity within industry as a result of the XP and Agile movements. The cited benefits are: improved software quality and increased responsiveness to changing customer requirements~\cite{WikiXP}. TDD further encourages the decomposition of software into smaller, independently verifiable modules, but goes further than this by stating that these tests should be written before the implementation.

@@

The Management API is provided as the interface to the core application logic and domain model. It is responsible for storage and retrieval of all entities such as hosts, services and their respective dependencies. These entities are exposed via the REST API to other parts of the application. The API accepts and responds with JSON\footnote{http://www.json.org/js.html} serialised data. The API is simple and discoverable, encouraging integration with other systems.

@@

Ruby on Rails is an extremely popular web framework written in Ruby. It provides a full suite of functionality from database access to view rendering. It has an extremely active community, over 3,400 contributors\cite{RailsContrib} and has been downloaded nearly 34 million times according to RubyGems.org~\cite{RailsPopularity}. It embraces common best practice patterns such as Model-View-Controller (MVC) and the ActiveRecord pattern~\cite{ActiveRecord}. Ruby on Rails was chosen for this project for the above reasons, as well as the excellent support for testing libraries such as RSpec.

@@

The pattern provides tight coupling between domain objects and the respective database tables that persist the data. ActiveRecord is a very convenient and low friction way of adding persistence to the application, but it has a few a disadvantages. It's main disadvantage is that it is very tightly coupled to the domain objects, this makes them harder to write isolated unit tests for, without extensive mocking of the database. There are, however, good solutions for the burden and fragility of database mocking within Ruby gems such as NullDB~\cite{NullDB}.

>>>>

The rise in software complexity together with ever changing business demands during its development has given rise to a number of popular methodologies or techniques in research and industry, such as Model Driven Development~\cite{ModelDrivenDevelopment}, Extreme Programming~\cite{BeckXP} and the Agile movement~\cite{AgileManifesto}.

@@

Test Driven Development (TDD) has surged in popularity within industry as a result of the XP and Agile movements. The cited benefits are: improved software quality and increased responsiveness to changing customer requirements~\cite{BeckTDD}. TDD further encourages the decomposition of software into smaller, independently verifiable modules, but goes further than this by stating that these tests should be written before the implementation.

@@

The Management API is provided as the interface to the core application logic and domain model. It is responsible for storage and retrieval of all entities such as hosts, services and their respective dependencies. These entities are exposed via the REST API to other parts of the application. The API accepts and responds with JSON\footnote{JSON - http://www.json.org/js.html} serialised data. The API is simple and discoverable, encouraging integration with other systems.

@@

Ruby on Rails\footnote{Ruby on Rails - http://rubyonrails.org/} is an extremely popular web framework written in Ruby. It provides a full suite of functionality from database access to view rendering. It has an extremely active community, over 3,400 contributors\cite{RailsContrib} and has been downloaded nearly 34 million times according to RubyGems.org~\cite{RailsPopularity}. It embraces common best practice patterns such as Model-View-Controller (MVC) and the ActiveRecord pattern~\cite{ActiveRecord}. Ruby on Rails was chosen for this project for the above reasons, as well as the excellent support for testing libraries such as RSpec\footnote{RSpec - https://relishapp.com/rspec}.

Sinatra\footnote{Sinatra - http://www.sinatrarb.com/} and Padrino\footnote{Padrino - http://www.padrinorb.com/} are alternative popular web frameworks for Ruby. Both of these frameworks are more minimal than Rails. They are useful for projects that are either especially simple, or projects that deviate from the standard Rails functionality by a large degree. This is not true of the monitoring API, it is a typical web application that can benefit from many of the framework features Rails offers, therefore it was deemed an appropriate choice for this component.

@@

The pattern provides tight coupling between domain objects and the respective database tables that persist the data. ActiveRecord is a very convenient and low friction way of adding persistence to the application, but it has a few a disadvantages. It's main disadvantage is that it is very tightly coupled to the domain objects, this makes them harder to write isolated unit tests for, without extensive mocking of the database. There are, however, good solutions for the burden and fragility of database mocking within Ruby gems such as FactoryGirl\footnote{FactoryGirl - https://github.com/thoughtbot/factory\_girl} and NullDB\footnote{NullDB - https://github.com/nulldb/nulldb}.
